Automatically Proving Equivalence by Type-Safe Reflection

### 2017-05-20 paper-CICM-17/content/3-hierarchyOfTactics.tex
Automatic reflection : the extension if now on the right to avoid the change of the index of the variables that were already there
CICM17 : Final version for Franck

Thanks to this encoding, we can now transform an \code{ExprG} from the group
level to an \code{ExprMo} at the monoid level. A constant $(\code{ConstG}\ p\
\Gamma\ c1)$ is transformed into the corresponding constant
$(\code{ConstMo}\ p\ \Gamma\ c1)$, a \code{PlusG} into the corresponding
\code{PlusMo}, a variable into the same variable, the negation of a
constant into the resulting constant, and finally the negation of a variable
$i$ into a $(\code{VarMo}\ p\ (\code{EncodingNegOfVar}\ \Gamma\ i))$.

@@

\begin{lstlisting}
%reflection reflectGroup : (p : Group c) $\rightarrow$ ($\Gamma$ : Vect n c) $\rightarrow$ 
                           (x : c) $\rightarrow$ ($\Gamma'$ ** ExprG p ($\Gamma'$ ++ $\Gamma$) x)
\end{lstlisting}

The \texttt{\%reflection} annotation means that Idris treats this as a 
compile time function on \emph{syntax}. Given a value of type
\texttt{c}, in some context $\Gamma$, it constructs a reflected expression 
in an extended context \texttt{$\Gamma'$ ++ $\Gamma$}. The context
contains references to subexpressions 
which are not themselves representable by \texttt{ExprG}.

>>>>

Thanks to this encoding, we can now transform an \code{ExprG} from the group
level to an \code{ExprMo} at the monoid level. A constant $(\code{ConstG}\ p\
\Gamma\ c1)$ is transformed into the corresponding constant
$(\code{ConstMo}\ \_\ \Gamma\ c1)$, a \code{PlusG} into the corresponding
\code{PlusMo}, a variable into the same variable, the negation of a
constant into the resulting constant, and finally the negation of a variable
$i$ into a $(\code{VarMo}\ \_\ (\code{EncodingNeg}\ \Gamma\ i))$.

@@

\begin{lstlisting}
%reflection reflectGroup : (p : Group c) $\rightarrow$ ($\Gamma$ : Vect n c) $\rightarrow$ 
                           (x : c) $\rightarrow$ ($\Gamma'$ ** ExprG p ($\Gamma$ ++ $\Gamma'$) x)
\end{lstlisting}

The \texttt{\%reflection} annotation means that Idris treats this as a 
compile time function on \emph{syntax}. Given a value of type
\texttt{c}, in some context $\Gamma$, it constructs a reflected expression 
in an extended context \texttt{$\Gamma$ ++ $\Gamma'$}. The context
contains references to subexpressions 
which are not themselves representable by \texttt{ExprG}.
